Solution to ``Chapter 2: Basic tail and concentration bounds"

### 2020-07-10 skills/math/tail_bound/tailbound_solution.tex
tail_boung

\paragraph{Solution:} 
\begin{enumerate}
	\item[(a)] Recall the proof of Markov's inequality. For any $t >0$,
	\[ \bbE[X] = \int_{0}^t x f_X(x) dx + \int_{t}^{+\infty} x f_X(x) dx \geq \int_{t}^{+\infty} x f_X(x)\geq t \int_{t}^{+\infty} f_X(x) = t \bbP( X \geq t).\]
	 If Markov's inequality meets the equality, the inequalities above should meet equality.

>>>>

\paragraph{Solution:} 
\begin{enumerate}
	\item[(a)] Recall the proof of Markov's inequality. For any $t >0$,
	\begin{equation}\label{eq:markov}
		\bbE[X] = \int_{0}^t x f_X(x) dx + \int_{t}^{+\infty} x f_X(x) dx \geq \int_{t}^{+\infty} x f_X(x)\geq t \int_{t}^{+\infty} f_X(x) = t \bbP( X \geq t).
	\end{equation}
	 If Markov's inequality meets the equality, the inequality~\eqref{eq:markov} meets the equality.
